---
title: "Plotting for simulation"
author: "Junting Ren"
date: "1/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../functions/SCB_dense.R")
source("../functions/SCB_to_CS.R")
source("../functions/noises.R") # for the noise functions
source("../functions/plot_cs.R") 
#library(SCBfda) # for the noise functions
library(SIRF)
library(tidyverse)
library(doParallel) # for parallel computing
library(cope)
library(patchwork)
library(latex2exp)
library(RColorBrewer)
date = "y2021_m01_d06"

```
# Dense functional data
## Demonstration of confidence sets in 1D
```{r}
save = T # whether to save the plots
load( paste( "dense_functional_sim.RData" ) )
N = NVec[2]
x = seq( 0, 1, length.out = 1000 )
dat_true = mu_ModelA(x)
set.seed(2022)
M = FunctionalDataSample( N =N,
                          x = x,
                          mu =mu_ModelA,
                          noise = BernsteinSumNoise,
                          sigma = sigma_ModelA,
                          sd_ObsNoise =0)
SCB = SCB_dense(M)
est_mean <- apply(M, 1, mean)
source("../functions/plot_cs.R") 
#debug(plot_cs)
plot_cs(SCB, levels = c(0.2,0.8, 0), x = x, y = x,mu_hat = est_mean, mu_true =  dat_true, together = F, xlab = "s")

if(save){
  ggsave("./figures/dense_1dshowcase.png")
}

```
Plotting idea for 1d: we have a vector of T or F same length of the x, then we can change this vector to ifelse(v, 1, 0)

## Demonstration of confidence sets in 2D
```{r}
N = NVec[4]
x = seq( 0, 1, length.out = 50 )
dat_true = mu_ModelB(x)
set.seed(2023)
M = FunctionalDataSample( N = N,
                          x = x,
                          mu =mu_ModelB,
                          noise = noise_ModelB,
                          sigma = sigma_ModelB,
                          sd_ObsNoise = 0 )
SCB = SCB_dense(M)
est_mean <- apply(M, 1:2, mean)
source("../functions/plot_cs.R") 
#debug(plot_cs)
p1 = plot_cs(SCB, levels = c(0.3,0.5,0.7), x = x, y = x, mu_true =  dat_true,mu_hat = est_mean, together = F, 
             xlab = TeX(r'($s_1$)'),ylab = TeX(r'($s_2$)'))
p2 = plot_cs(SCB, levels = c(0.3,0.5,0.7), x = x, y = x, mu_true =  dat_true,mu_hat = est_mean, together = T,
             xlab = TeX(r'($s_1$)'),ylab = TeX(r'($s_2$)'))
p = p2/p1
p
if(save){
  ggsave("./figures/dense_2dshowcase.png", plot = p, width = unit(10, "cm"), height = unit(7, "cm"))
}
```


## Dense functional data result plotting
```{r}
level = 0.95
load("dense_functional_sim_1D_cope.RData")
#1D
df_result_sim = result_frame_1d %>%
  select(N, SCI = SCB, Upper1000, Upper100, Upper25, Upper10, Upper5, cope5, cope10, cope25)%>% 
  pivot_longer(!c(N), names_to = "Simulation", values_to = "coverage_rate") %>% 
  mutate(coverage_rate = coverage_rate*100,
         N = as_factor(N),
         Simulation = fct_relevel(Simulation, levels = c("Upper5","Upper10",  
                                                         "Upper25", "Upper100",
                                                         "Upper1000","SCI", 
                                                         "cope25","cope10","cope5"
                                                          )))
  
mypal <- colorRampPalette(brewer.pal(6, "PuBu"))
mypal2 <- colorRampPalette(rev(brewer.pal(6, "YlOrRd")))
result_sim_plotA = df_result_sim %>% ggplot(aes(x = N, y = coverage_rate,group = Simulation,color = Simulation)) + 
  geom_line()+
  geom_point(aes(shape = Simulation)) +
  scale_shape_manual(values = c(rep(1,6), rep(2, 4)),
                     labels = c(TeX("$5$ levels"),TeX("$10$ levels"), 
                                TeX("$25$ levels"),TeX(" $10 ^2$ levels"),
                                TeX(" $10^3$ levels"),"SCI", 
                                "25 levels bonf","10 levels bonf","5 levels bonf")
  ) +
  scale_colour_manual(values = c(mypal(6), mypal2(4)),
                      labels = c(TeX("$5$ levels"),TeX("$10$ levels"), 
                                 TeX("$25$ levels"),TeX(" $10 ^2$ levels"),
                                 TeX(" $10^3$ levels"),"SCI", 
                                 "25 levels bonf","10 levels bonf","5 levels bonf")
  ) +
  ylim(c(69,100)) +
  geom_hline(yintercept = 100*(level+c(-2,2)*sqrt(level*(1-level)/n_sim)), linetype = 'dashed')+
  theme_light() +
  ggtitle("1D dense data coverage rate")+
  theme(legend.position = c(0.75, 0.25),legend.key.size = unit(0.2, 'cm')) +
  ylab("Coverage rate")+ 
  xlab("Number of samples N") +
  theme(axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5),
        text = element_text(size = 13))

# df_result_sim = result_frame_1d %>% 
#   select(N, SCI = SCB, Upper1000, Upper100, Upper25, Upper10, Upper5)%>% 
#   pivot_longer(!c(N), names_to = "Simulation", values_to = "coverage_rate") %>% 
#   mutate(coverage_rate = coverage_rate*100,
#          N = as_factor(N),
#          Simulation = fct_relevel(Simulation, levels = rev(c("SCI", "Upper1000",
#                                                          "Upper100", "Upper25",
#                                                          "Upper10", "Upper5"))))
# 
# result_sim_plotA = df_result_sim %>% ggplot(aes(x = N, y = coverage_rate,group = Simulation,color = Simulation)) + 
#   geom_line()+
#   geom_point() +ylim(c(84,100)) +
#   geom_hline(yintercept = 100*(level+c(-2,2)*sqrt(level*(1-level)/n_sim)), linetype = 'dashed')+
#   # scale_colour_discrete(labels = c("SCB", TeX(" $10^3$ levels"), 
#   #                                  TeX(" $10 ^2$ levels"), TeX("$25$ levels"),
#   #                                  TeX("$10$ levels"), TeX("$5$ levels"))) +
#   theme_light() +
#   ylim(c(69,100)) +
#   ggtitle("1D dense data coverage rate")+
#   theme(legend.position = c(0.75, 0.2),legend.key.size = unit(0.2, 'cm'),
#         plot.title = element_text(face = "bold", hjust = 0.5)) +
#   ylab("Coverage rate") +
#   xlab("Number of samples N") +
#   scale_color_brewer(labels = rev(c("SCI", TeX(" $10^3$ levels"), 
#                                     TeX(" $10 ^2$ levels"), TeX("$25$ levels"),
#                                     TeX("$10$ levels"), TeX("$5$ levels"))),palette = "PuBu", direction = 1)


#2D
load( paste( "dense_functional_sim.RData" ) )
df_result_sim = result_frame_2d %>%
  select(N, SCI = SCB, Upper1000, Upper100, Upper25, Upper10, Upper5, cope5, cope10, cope25)%>% 
  pivot_longer(!c(N), names_to = "Simulation", values_to = "coverage_rate") %>% 
  mutate(coverage_rate = coverage_rate*100,
         N = as_factor(N),
         Simulation = fct_relevel(Simulation, levels = c("Upper5","Upper10",  
                                                         "Upper25", "Upper100",
                                                         "Upper1000","SCI", 
                                                         "cope25","cope10","cope5"
                                                          )))
  
mypal <- colorRampPalette(brewer.pal(6, "PuBu"))
mypal2 <- colorRampPalette(rev(brewer.pal(6, "YlOrRd")))
result_sim_plotB = df_result_sim %>% ggplot(aes(x = N, y = coverage_rate,group = Simulation,color = Simulation)) + 
  geom_line()+
  geom_point(aes(shape = Simulation)) +
  scale_shape_manual(values = c(rep(1,6), rep(2, 4)),
                     labels = c(TeX("$5$ levels"),TeX("$10$ levels"), 
                                TeX("$25$ levels"),TeX(" $10 ^2$ levels"),
                                TeX(" $10^3$ levels"),"SCI", 
                                "25 levels bonf","10 levels bonf","5 levels bonf")
  ) +
  scale_colour_manual(values = c(mypal(6), mypal2(4)),
                      labels = c(TeX("$5$ levels"),TeX("$10$ levels"), 
                                 TeX("$25$ levels"),TeX(" $10 ^2$ levels"),
                                 TeX(" $10^3$ levels"),"SCI", 
                                 "25 levels bonf","10 levels bonf","5 levels bonf")
  ) +
  ylim(c(69,100)) +
  geom_hline(yintercept = 100*(level+c(-2,2)*sqrt(level*(1-level)/n_sim)), linetype = 'dashed')+
  theme_light() +
  ggtitle("2D dense data coverage rate")+
  theme(legend.position = c(0.75, 0.25),legend.key.size = unit(0.2, 'cm')) +
  ylab("Coverage rate")+ 
  xlab("Number of samples N") +
  theme(axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5),
        text = element_text(size = 13))
result_sim_plotA + result_sim_plotB
if(save){
 ggsave("./figures/dense_1_and_2dsim_results.png", width = unit(10, "cm"), height = unit(5, "cm")) 
}
```

Simulation coverage table for 1D
```{r}
knitr::kable(result_frame_1d)
```

Simulation coverage table for 2D
```{r}
knitr::kable(result_frame_2d)
```


# Regression outcome simulation
```{r}
load("regression_outcome_bootstrap.RData")
```


## Demonstration of linear regression outcome with 2 covariates
```{r}
source("../functions/plot_cs.R") 
source("../functions/SCB_to_CS.R")
library(patchwork)
beta = c(-1,1,0.5,-1.1, -0.5, 0.8, -1.1)
n_boot = 2000
alpha = 0.05
sd_error = 2
model = "y ~ poly(x1,3)+poly(x2,3)"
x1 =  seq(-1,1,length.out = 100)
x2 = seq(-1,1,length.out = 100)
grid_df = data.frame( expand.grid(x1 = x1, x2 =  x2) )# dataset for model fit inside the function
pred_data =as.matrix(cbind(x0 = rep(1,100*100), expand.grid(x1 = x1, x2 =  x2) )) # for producing the true mean
# generate the true mean for checking the containment
y_true_pred_data = pred_data[,1]*beta[1] + pred_data[,2]*beta[2]+(pred_data[,2]^2)*beta[3] +(pred_data[,2]^3)*beta[4] +
  (pred_data[,3])*beta[5] +  (pred_data[,3]^2)*beta[6] +  (pred_data[,3]^3)*beta[7]
true_mean_matrix = data.frame(pred_data, y_true = y_true_pred_data) %>% dplyr::select(x1,x2, y_true)%>% 
  pivot_wider(names_from = x2, values_from = y_true) %>% column_to_rownames("x1") %>% as.matrix()
n = 500
X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 =  rnorm(n))
set.seed(2022)
y =  X[,1]*beta[1] + X[,2]*beta[2]+(X[,2]^2)*beta[3] +(X[,2]^3)*beta[4] +
  (X[,3])*beta[5] +  (X[,3]^2)*beta[6] +  (X[,3]^3)*beta[7]+ rnorm(n, sd=sd_error)
data_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
SCB = cbind(SCB_linear_outcome(df_fit = data_fit, model = model, grid_df = grid_df, n_boot = n_boot, alpha = alpha),y_true = y_true_pred_data)
scb_up_matrix = SCB %>% select(x1,x2, UpperBound)%>% 
      pivot_wider(names_from = x2, values_from = UpperBound) %>% column_to_rownames("x1") %>% as.matrix()
est_matrix = SCB %>% select(x1,x2, Mean)%>% 
      pivot_wider(names_from = x2, values_from = Mean) %>% column_to_rownames("x1") %>% as.matrix()
scb_low_matrix = SCB %>% select(x1,x2, LowerBound)%>% 
      pivot_wider(names_from = x2, values_from = LowerBound) %>% column_to_rownames("x1") %>% as.matrix()
confidence_set = scb_to_cs(scb_up_matrix,scb_low_matrix, levels = c(-1,-0.5,0),x1 = x1, x2 = x2,
                              true_mean = true_mean_matrix,est_mean = est_matrix, return_contain_only = T, return_plot = T, xlab = TeX(r'($x_1$)'), ylab = TeX(r'($x_2$)'))
p = confidence_set$plot_cs[[1]]/confidence_set$plot_cs[[2]]
p
if(save){
  ggsave("./figures/linear_regression_outcome_showcase.png", plot = p, width = unit(10, "cm"), height = unit(7, "cm"))
}
```

```{r}
fit = lm(as.formula(model), data_fit)
cov_beta = vcov(fit)
X_design = model.matrix(formula(~ poly(x1,3)+poly(x2,3)), data = data.frame(pred_data))
cov_pred = X_design %*% cov_beta %*% t(X_design)
cor_pred = cov2cor(cov_pred)
diag(cor_pred) = NA
mean(cor_pred, na.rm = T)
```

## Demonstration of logistics regression outcome with 2 covariates
```{r}
beta = c(-1,1,0.5,-1.1, -0.5, 0.8, -1.1)
model = "y ~ poly(x1,3) + poly(x2,3)"
# alpha = 0.05
# n_boot = 1000
x1 =  seq(-1,1,length.out = 100)
x2 = seq(-1,1,length.out = 100)
grid_df = data.frame( expand.grid(x1 = x1, x2 =  x2) )# dataset for model fit inside the function
pred_data =as.matrix(cbind(x0 = rep(1,100*100), expand.grid(x1 = x1, x2 =  x2) )) # for producing the true mean
y_true_pred_data = expit(pred_data[,1]*beta[1] + pred_data[,2]*beta[2]+(pred_data[,2]^2)*beta[3] +(pred_data[,2]^3)*beta[4] +
  (pred_data[,3])*beta[5] +  (pred_data[,3]^2)*beta[6] +  (pred_data[,3]^3)*beta[7])
true_mean_matrix = data.frame(pred_data, y_true = y_true_pred_data) %>% dplyr::select(x1,x2, y_true)%>% 
      pivot_wider(names_from = x2, values_from = y_true) %>% column_to_rownames("x1") %>% as.matrix()
n = 500
X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
linear = X[,1]*beta[1] + X[,2]*beta[2]+(X[,2]^2)*beta[3] +(X[,2]^3)*beta[4] +
  (X[,3])*beta[5] +  (X[,3]^2)*beta[6] +  (X[,3]^3)*beta[7]
y = rep(0,n)
y_true = rep(0,n)
set.seed(2022)
for(i in 1:n){
  y[i] = rbinom(1,1, prob = 1/(1+exp(-linear[i])))
  y_true[i] = 1/(1+exp(-linear[i]))
}
df_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
SCB = cbind(SCB_logistic_outcome(df_fit = df_fit, model = model, grid_df = grid_df, n_boot = n_boot, alpha = alpha), 
            y_true_pred_data) 
scb_up_matrix = SCB %>% select(x1,x2, UpperBound)%>%
  pivot_wider(names_from = x2, values_from = UpperBound) %>% column_to_rownames("x1") %>% as.matrix()
est_matrix = SCB %>% select(x1,x2, Mean)%>% 
      pivot_wider(names_from = x2, values_from = Mean) %>% column_to_rownames("x1") %>% as.matrix()
scb_low_matrix = SCB %>% select(x1,x2, LowerBound)%>%
  pivot_wider(names_from = x2, values_from = LowerBound) %>% column_to_rownames("x1") %>% as.matrix()
confidence_set = scb_to_cs(scb_up_matrix,scb_low_matrix, levels = c(0.4,0.5, 0.6),x1 = x1, x2 = x2,est_mean = est_matrix,true_mean = true_mean_matrix, return_contain_only = T, return_plot = T,
                           xlab = TeX(r'($x_1$)'), ylab = TeX(r'($x_2$)'))
p = confidence_set$plot_cs[[1]]/confidence_set$plot_cs[[2]]
p
if(save){
  ggsave("./figures/logistic_regression_outcome_showcase.png", plot = p, width = unit(10, "cm"), height = unit(7, "cm"))
}
```


```{r}
fit_glm = glm(as.formula(model), df_fit,family = binomial())
cov_beta_glm = vcov(fit_glm)
X_design_glm = model.matrix(formula(~ poly(x1,3)+poly(x2,3)), data = data.frame(pred_data))
cov_pred_glm = X_design_glm %*% cov_beta_glm %*% t(X_design_glm)
cor_pred_glm = cov2cor(cov_pred_glm)
diag(cor_pred_glm) = NA
sample_indx = sample(1:length(c(cor_pred_glm[cor_pred_glm!=0])), 10000)
df_cor = data.frame(Logistic = abs(c(cor_pred_glm[cor_pred_glm!=0])[sample_indx]),
                    Linear = abs(c(cor_pred[cor_pred!=0])[sample_indx])) %>% 
  pivot_longer(everything(), names_to = "Model", values_to = "Correlation") %>% 
  distinct()

```

## Simulation result for regression outcome
```{r}
load("regression_outcome_bootstrap2.RData")
level = 0.95
#Linear
result_df_linear_final = result_df_linear
df_result_sim = result_df_linear %>% 
  mutate(SCI = scb) %>% filter(N !=50) %>% 
  select(N, SCI, Upper1000, Upper100, Upper25, Upper10, Upper5)%>% 
  pivot_longer(!c(N), names_to = "Simulation", values_to = "coverage_rate") %>% 
  mutate(coverage_rate = coverage_rate*100,
         N = as_factor(N),
         Simulation = fct_relevel(Simulation, levels = rev(c("SCI", "Upper1000",
                                                         "Upper100", "Upper25",
                                                         "Upper10", "Upper5"))))

result_sim_linear = df_result_sim %>% ggplot(aes(x = N, y = coverage_rate,group = Simulation,color = Simulation)) + 
  geom_line()+
  geom_point() +
  ylim(c(90,100)) +
  geom_hline(yintercept = 100*(level+c(-2,2)*sqrt(level*(1-level)/n_sim)), linetype = 'dashed')+
  # scale_colour_discrete(labels = c("SCB", TeX(" $10^3$ levels"), 
  #                                  TeX(" $10 ^2$ levels"), TeX("$25$ levels"),
  #                                  TeX("$10$ levels"), TeX("$5$ levels"))) +
  theme_light() +
  ggtitle("Linear regression")+
  theme(legend.position = c(0.75, 0.2),legend.key.size = unit(0.2, 'cm'),
        plot.title = element_text(face = "bold", hjust = 0.5),
        text = element_text(size = 13)) +
  ylab("Coverage rate") +
  xlab("Number of samples N") +
  scale_color_brewer(labels = rev(c("SCB", TeX(" $10^3$ levels"), 
                                    TeX(" $10 ^2$ levels"), TeX("$25$ levels"),
                                    TeX("$10$ levels"), TeX("$5$ levels"))),
                     palette = "PuBu", direction = 1)

load("regression_outcome_bootstrap.RData")
result_df_logistic_final = result_df_logistic
#Logistic
df_result_sim = result_df_logistic %>%
  mutate(SCI = scb) %>% filter(N !=50) %>% 
  select(N, SCI, Upper1000, Upper100, Upper25, Upper10, Upper5)%>% 
  pivot_longer(!c(N), names_to = "Simulation", values_to = "coverage_rate") %>% 
  mutate(coverage_rate = coverage_rate*100,
         N = as_factor(N),
         Simulation = fct_relevel(Simulation, levels = rev(c("SCI", "Upper1000",
                                                         "Upper100", "Upper25",
                                                         "Upper10", "Upper5"))))
  
result_sim_logistic = df_result_sim %>% ggplot(aes(x = N, y = coverage_rate,group = Simulation,color = Simulation)) + 
  geom_line()+
  geom_point() +
  ylim(c(90,100)) +
  geom_hline(yintercept = 100*(level+c(-2,2)*sqrt(level*(1-level)/n_sim)), linetype = 'dashed')+
  # scale_colour_discrete(labels = c("SCB", TeX(" $10^3$ levels"), 
  #                                  TeX(" $10 ^2$ levels"), TeX("$25$ levels"),
  #                                  TeX("$10$ levels"), TeX("$5$ levels"))) +
  theme_light() +
  ggtitle("Logistic regression")+
  theme(legend.position = c(0.75, 0.2),legend.key.size = unit(0.2, 'cm'),
        plot.title = element_text(face = "bold", hjust = 0.5),
        text = element_text(size = 13)) +
  ylab("Coverage rate") +
  xlab("Number of samples N") +
  scale_color_brewer(labels = rev(c("SCI", TeX(" $10^3$ levels"), 
                                    TeX(" $10 ^2$ levels"), TeX("$25$ levels"),
                                    TeX("$10$ levels"), TeX("$5$ levels"))),
                     palette = "PuBu", direction = 1)+ 
  theme(axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5))
#result_sim_linear + result_sim_logistic



result_sim_linear + result_sim_logistic
if(save){
 ggsave("./figures/regression_outcome_results.png", width = unit(10, "cm"), height = unit(5, "cm")) 
}

```
Linear results
```{r}
result_df_linear_final
```


Logistic results
```{r}
result_df_logistic_final
```



# Regression coefficient simulations
```{r}
load("regression_coef_result.RData")
source("../functions/SCB_dense.R")
source("../functions/SCB_to_CS.R")
source("../functions/noises.R") # for the noise functions
source("../functions/plot_cs.R") 
```

## showcase of coefficient discret confidence set
```{r}
n = 500
X = cbind(rep(1,n), MASS::mvrnorm(n = n, mu = rep(0,dim(covariance)[1]),Sigma = covariance))
set.seed(2022)
y = X %*% beta +rnorm(n, sd = sd_error)
df_fit = data.frame(y= y, X[,-1])
SCB = cbind(SCB_regression_coef(df_fit = df_fit, model = model, n_boot = n_boot, alpha = 0.05), beta_true = beta)
beta_names = paste("beta", 0:(M-1),sep = "")

#debug(plot_cs)
plot_cs(SCB = list(scb_up = SCB$UpperBound, scb_low = SCB$LowerBound), x = beta_names,levels = c(-2, -0.5, -0.1, 0.2), mu_true = beta, mu_hat = SCB$Mean)
if(save){
 ggsave("./figures/coeff_showcase.png") 
}
```
black point are the estimated mean, gray are the true points.

## Correlation for coefficients
```{r}
fit_coef = lm(y~., df_fit)
cor_coef = cov2cor(vcov(fit_coef))
diag(cor_coef) = NA
df_cor_coef = data.frame(Model = "Discrete\ncoefficient", Correlation = c(abs(cor_coef))) %>% unique()
rbind(df_cor, df_cor_coef) %>% ggplot(aes(x = Correlation, fill = Model)) +
  geom_histogram(aes(y=..density..),bins = 100, 
                 alpha = 0.3,position = "identity")+
  geom_density(alpha=0.3) + theme_light() + labs(y = "Density", x = "Absolute pairwise correlations")+
  ggtitle("")+theme(plot.title = element_text(face = "bold", hjust = 0.5), text = element_text(size = 13))
if(save){
  ggsave("./figures/correlation_diff_lm_glm.png", width = unit(10, "cm"), height = unit(7, "cm"))
}
```


## Simulation results for regression coefficients
```{r}
level = 0.95
#Linear
df_result_sim = result_df_diff_beta %>% 
  mutate(SCI = scb) %>% 
  select(beta_num, SCI, upper1000, upper100, upper25,upper5000, upper8000)%>% 
  pivot_longer(!c(beta_num), names_to = "Simulation", values_to = "coverage_rate") %>% 
  mutate(coverage_rate = coverage_rate*100,
         beta_num = as_factor(beta_num),
         Simulation = fct_relevel(Simulation, 
                                  levels=rev(c("SCI","upper8000",
                                               "upper5000","upper1000",
                                               "upper100", "upper25"))))

result_sim_beta_num = df_result_sim %>% ggplot(aes(x = beta_num, y = coverage_rate,group = Simulation,color = Simulation)) + 
  geom_line()+
  geom_point() +
  ylim(c(90,100)) +
  geom_hline(yintercept = 100*(level+c(-2,2)*sqrt(level*(1-level)/n_sim)), linetype = 'dashed')+
  # scale_colour_discrete(labels = c("SCB", TeX(" $10^3$ levels"), 
  #                                  TeX(" $10 ^2$ levels"), TeX("$25$ levels"),
  #                                  TeX("$10$ levels"), TeX("$5$ levels"))) +
  theme_light() +
  ggtitle("Regression cofficient for N=500")+
  theme(legend.position = c(0.75, 0.2),legend.key.size = unit(0.2, 'cm'),
        plot.title = element_text(face = "bold", hjust = 0.5)) +
  ylab("Coverage rate") +
  xlab("Number of coefficents M") +
  scale_color_brewer(labels = rev(c("SCI",TeX(" $8 \\times 10^3$ levels"),
                                    TeX(" $5 \\times 10^3$ levels"), 
                                    TeX(" $10^3$ levels"), 
                                    TeX(" $10 ^2$ levels"), TeX("$25$ levels"))),
                     palette = "PuBu", direction = 1)


#Logistic
df_result_sim = result_df_diff_n %>%
  mutate(SCI = scb) %>% filter(N !=200) %>% 
  select(N, SCI, upper1000, upper100, upper25,upper5000, upper8000)%>% 
  pivot_longer(!c(N), names_to = "Simulation", values_to = "coverage_rate") %>% 
  mutate(coverage_rate = coverage_rate*100,
         N = as_factor(N),
         Simulation = fct_relevel(Simulation, 
                                  levels=rev(c("SCI","upper8000",
                                               "upper5000","upper1000",
                                               "upper100", "upper25"))))
  
result_sim_n_beta= df_result_sim %>% ggplot(aes(x = N, y = coverage_rate,group = Simulation,color = Simulation)) + 
  geom_line()+
  geom_point() +
  ylim(c(90,100)) +
  geom_hline(yintercept = 100*(level+c(-2,2)*sqrt(level*(1-level)/n_sim)), linetype = 'dashed')+
  # scale_colour_discrete(labels = c("SCB", TeX(" $10^3$ levels"), 
  #                                  TeX(" $10 ^2$ levels"), TeX("$25$ levels"),
  #                                  TeX("$10$ levels"), TeX("$5$ levels"))) +
  theme_light() +
  ggtitle("Regression cofficient for M=50")+
  theme(legend.position = c(0.75, 0.2),legend.key.size = unit(0.2, 'cm'),
        plot.title = element_text(face = "bold", hjust = 0.5)) +
  ylab("Coverage rate") +
  xlab("Number of samples N") +
  scale_color_brewer(labels = rev(c("SCI",TeX(" $8 \\times 10^3$ levels"),
                                    TeX(" $5 \\times 10^3$ levels"), 
                                    TeX(" $10^3$ levels"), 
                                    TeX(" $10 ^2$ levels"), TeX("$25$ levels"))),
                     palette = "PuBu", direction = 1)+ 
  theme(axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5))
result_sim_beta_num + result_sim_n_beta
if(save){
 ggsave("./figures/regression_coeff_results.png", width = unit(10, "cm"), height = unit(5, "cm")) 
}
```
Sample size results
```{r}
result_df_diff_n
```

Number of coefficient results
```{r}
result_df_diff_beta
```

