---
title: "Simulation_analysis_regression_outcome_discrete_grid Table 2"
author: "Junting Ren"
date: "12/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(doParallel) # for parallel computing
source("../functions/SCB_dense.R")
source("../functions/SCB_to_CS.R")
source("../functions/plot_cs.R")
source("../functions/noises.R") # for the noise functions
source("../functions/regression_outcome_scb.R")
```


# This simulation replicates Paper's Table 2 result
Table 2. Simulation Coverage rates for fix grid step size for linear regression model.

# linear regression simulation for confidence set
Here is the model we are going to simulate from 
$$
y = \beta_0 + \beta_1 x_1 + \beta_2x_1^2 + \beta_3x_1^3+\beta_4 x_2 + \beta_5 x_2^2 + \beta_6x_2^3 + \epsilon
$$
The plotting is going to be a 2d plane (x1, x2) with colors indicating the y values.

```{r}
save = T
num_levels = 5000
n_sim = 5000
n = 300 #number of sample to fit the model
N_pred =c(5, 10,20, 50,80)# number of predictions to do is 5*5 or 10*10, a grid
beta = c(-1,1,0.5,-1.1, -0.5, 0.8, -1.1)
n_boot = 2000
alpha = 0.05
sd_error = 2
model = "y ~ poly(x1,3)+poly(x2,3)"
random_level = T #whether the levels are random or just quantiles of the data
```



## Start the simulation
```{r}
cl <- makeCluster(detectCores()-1)
registerDoParallel(cl)
scb_contain_v = c()
upper5000_contain_v = c()
upper1000_contain_v = c()
upper500_contain_v = c()
upper200_contain_v = c()
upper100_contain_v = c()
upper50_contain_v = c()
upper25_contain_v = c()
upper10_contain_v = c()
upper5_contain_v = c()

for(n_pred in N_pred){
  length_one_side = n_pred/2*0.02
  x1 =  seq(-length_one_side,length_one_side,length.out = n_pred)
  x2 = seq(-length_one_side,length_one_side,length.out = n_pred)
  grid_df = data.frame( expand.grid(x1 = x1, x2 =  x2) )# dataset for model fit inside the function
  pred_data =as.matrix(cbind(x0 = rep(1,length(x1)*length(x1)), expand.grid(x1 = x1, x2 =  x2) )) # for producing the true mean
  # generate the true mean for checking the containment
  y_true_pred_data = pred_data[,1]*beta[1] + pred_data[,2]*beta[2]+(pred_data[,2]^2)*beta[3] +(pred_data[,2]^3)*beta[4] +
    (pred_data[,3])*beta[5] +  (pred_data[,3]^2)*beta[6] +  (pred_data[,3]^3)*beta[7]
  true_mean_matrix = data.frame(pred_data, y_true = y_true_pred_data) %>% dplyr::select(x1,x2, y_true)%>% 
    pivot_wider(names_from = x2, values_from = y_true) %>% column_to_rownames("x1") %>% as.matrix()
  levels = seq(min(y_true_pred_data), max(y_true_pred_data), length.out = num_levels)
  p_result = foreach(t=1:n_sim,.errorhandling = "pass", 
                          .inorder = F,.verbose	=F, .packages = "tidyverse", .export = "plot_cs") %dopar% {
    #X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
    X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 =  rnorm(n))
    y =  X[,1]*beta[1] + X[,2]*beta[2]+(X[,2]^2)*beta[3] +(X[,2]^3)*beta[4] +
      (X[,3])*beta[5] +  (X[,3]^2)*beta[6] +  (X[,3]^3)*beta[7]+ rnorm(n, sd=sd_error)
    data_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
    SCB =  cbind(SCB_linear_outcome(df_fit = data_fit, model = model, grid_df = grid_df, n_boot = n_boot, alpha = alpha),y_true = y_true_pred_data)
    scb_up_matrix = SCB %>% select(x1,x2, UpperBound)%>% 
      pivot_wider(names_from = x2, values_from = UpperBound) %>% column_to_rownames("x1") %>% as.matrix()
    scb_low_matrix = SCB %>% select(x1,x2, LowerBound)%>% 
      pivot_wider(names_from = x2, values_from = LowerBound) %>% column_to_rownames("x1") %>% as.matrix()
    confidence_set = scb_to_cs(scb_up_matrix,scb_low_matrix, levels = levels,
                               true_mean = true_mean_matrix, return_contain_only = T)
    upper5000 = confidence_set$contain_all
    if(random_level){
      upper1000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 1000)])
      upper500= all(confidence_set$contain_individual[sample(1:num_levels, size = 500)])
      upper200 = all(confidence_set$contain_individual[sample(1:num_levels, size = 200)])
      upper100 = all(confidence_set$contain_individual[sample(1:num_levels, size = 100)])
      upper50 = all(confidence_set$contain_individual[sample(1:num_levels, size = 50)])
      upper25 = all(confidence_set$contain_individual[sample(1:num_levels, size = 25)])
      upper10 = all(confidence_set$contain_individual[sample(1:num_levels, size = 10)])
      upper5 = all(confidence_set$contain_individual[sample(1:num_levels, size = 5)])
    }else{
      upper1000 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 1000)])
      upper500= all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 500)])
      upper200 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 200)])
      upper100 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 100)])
      upper50 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 50)])
      upper25 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 25)])
      upper10 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 10)])
      upper5 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 5)])
    }
    cover_scb  = SCB %>% 
      mutate(contain = y_true >= LowerBound & y_true <= UpperBound) %>% 
      pull(contain) %>% 
      all()
    list(upper5000 = upper5000, upper1000= upper1000,
         upper500= upper500, upper200 = upper200,
         upper100 = upper100, upper50 = upper50,
         upper25 = upper25,
         upper10 = upper10, upper5 =upper5,
         cover_scb =cover_scb
         )
    # list(cover_scb = cover_scb)
  }
  scb_contain_v = c(scb_contain_v,mean(sapply(p_result, function(x) x$cover_scb)))
  upper5000_contain_v = c(upper5000_contain_v, mean(sapply(p_result, function(x) x$upper5000)))
  upper1000_contain_v = c(upper1000_contain_v, mean(sapply(p_result, function(x) x$upper1000)))
  upper500_contain_v = c(upper500_contain_v, mean(sapply(p_result, function(x) x$upper500)))
  upper200_contain_v = c(upper200_contain_v, mean(sapply(p_result, function(x) x$upper200)))
  upper100_contain_v = c(upper100_contain_v, mean(sapply(p_result, function(x) x$upper100)))
  upper50_contain_v = c(upper50_contain_v, mean(sapply(p_result, function(x) x$upper50)))
  upper25_contain_v = c(upper25_contain_v, mean(sapply(p_result, function(x) x$upper25)))
  upper10_contain_v = c(upper10_contain_v, mean(sapply(p_result, function(x) x$upper10)))
  upper5_contain_v = c(upper5_contain_v, mean(sapply(p_result, function(x) x$upper5)))
}

result_df_linear_pred_num = data.frame(N_pred =N_pred,
           Upper5 = upper5_contain_v,
           Upper10 = upper10_contain_v,
           Upper25 = upper25_contain_v,
           Upper50 = upper50_contain_v,
           Upper100 = upper100_contain_v,
           Upper200 = upper200_contain_v,
           Upper500 = upper500_contain_v,
           Upper1000 = upper1000_contain_v,
           upper5000 = upper5000_contain_v,
           scb = scb_contain_v
           )
result_df_linear_pred_num
```


# Logistic regression
```{r}
# have to make sure that extreme values do not overshoots the expit, or else the model will not be able to estimate the coeffcient accurately.
beta = c(-1,1,0.5,-1.1, -0.5, 0.8, -1.1)
```



## Start the simulation
```{r}
scb_contain_v = c()
upper5000_contain_v = c()
upper1000_contain_v = c()
upper500_contain_v = c()
upper200_contain_v = c()
upper100_contain_v = c()
upper50_contain_v = c()
upper25_contain_v = c()
upper10_contain_v = c()
upper5_contain_v = c()

for(n_pred in N_pred){
  length_one_side = n_pred/2*0.02
  x1 =  seq(-length_one_side,length_one_side,length.out = n_pred)
  x2 = seq(-length_one_side,length_one_side,length.out = n_pred)
  grid_df = data.frame( expand.grid(x1 = x1, x2 =  x2) )# dataset for model fit inside the function
  pred_data =as.matrix(cbind(x0 = rep(1,length(x1)*length(x1)), expand.grid(x1 = x1, x2 =  x2) )) # for producing the true mean
  y_true_pred_data = expit(pred_data[,1]*beta[1] + pred_data[,2]*beta[2]+(pred_data[,2]^2)*beta[3] +(pred_data[,2]^3)*beta[4] +
                             (pred_data[,3])*beta[5] +  (pred_data[,3]^2)*beta[6] +  (pred_data[,3]^3)*beta[7])
  levels = seq(min(y_true_pred_data), max(y_true_pred_data), length.out = num_levels)
  true_mean_matrix = data.frame(pred_data, y_true = y_true_pred_data) %>% dplyr::select(x1,x2, y_true)%>% 
    pivot_wider(names_from = x2, values_from = y_true) %>% column_to_rownames("x1") %>% as.matrix()
  p_result = foreach(t=1:n_sim,.errorhandling = "pass", 
                          .inorder = F,.verbose	=F, .packages = "tidyverse", .export = "plot_cs") %dopar% {
    #X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
    X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 =  rnorm(n))
    linear =  X[,1]*beta[1] + X[,2]*beta[2]+(X[,2]^2)*beta[3] +(X[,2]^3)*beta[4] +
      (X[,3])*beta[5] +  (X[,3]^2)*beta[6] +  (X[,3]^3)*beta[7]
    y = rep(0,n)
    for(i in 1:n){
      y[i] = rbinom(1,1, prob = 1/(1+exp(-linear[i])))
    }
    df_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
    SCB = cbind(SCB_logistic_outcome(df_fit = df_fit, model = model, grid_df = grid_df, n_boot = n_boot, alpha = alpha),y_true = y_true_pred_data)
    scb_up_matrix = SCB %>% select(x1,x2, UpperBound)%>% 
      pivot_wider(names_from = x2, values_from = UpperBound) %>% column_to_rownames("x1") %>% as.matrix()
    scb_low_matrix = SCB %>% select(x1,x2, LowerBound)%>% 
      pivot_wider(names_from = x2, values_from = LowerBound) %>% column_to_rownames("x1") %>% as.matrix()
    confidence_set = scb_to_cs(scb_up_matrix,scb_low_matrix, levels = levels,
                               true_mean = true_mean_matrix, return_contain_only = T)
    upper5000 = confidence_set$contain_all
    if(random_level){
      upper1000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 1000)])
      upper500= all(confidence_set$contain_individual[sample(1:num_levels, size = 500)])
      upper200 = all(confidence_set$contain_individual[sample(1:num_levels, size = 200)])
      upper100 = all(confidence_set$contain_individual[sample(1:num_levels, size = 100)])
      upper50 = all(confidence_set$contain_individual[sample(1:num_levels, size = 50)])
      upper25 = all(confidence_set$contain_individual[sample(1:num_levels, size = 25)])
      upper10 = all(confidence_set$contain_individual[sample(1:num_levels, size = 10)])
      upper5 = all(confidence_set$contain_individual[sample(1:num_levels, size = 5)])
    }else{
      upper1000 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 1000)])
      upper500= all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 500)])
      upper200 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 200)])
      upper100 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 100)])
      upper50 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 50)])
      upper25 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 25)])
      upper10 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 10)])
      upper5 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 5)])
    }
    cover_scb  = SCB %>% 
      mutate(contain = y_true >= LowerBound & y_true <= UpperBound) %>% 
      pull(contain) %>% 
      all()
    list(upper5000 = upper5000, upper1000= upper1000,
         upper500= upper500, upper200 = upper200,
         upper100 = upper100, upper50 = upper50,
         upper25 = upper25,
         upper10 = upper10, upper5 =upper5,
         cover_scb =cover_scb
         )
    # list(cover_scb = cover_scb)
  }
  scb_contain_v = c(scb_contain_v,mean(sapply(p_result, function(x) x$cover_scb)))
  upper5000_contain_v = c(upper5000_contain_v, mean(sapply(p_result, function(x) x$upper5000)))
  upper1000_contain_v = c(upper1000_contain_v, mean(sapply(p_result, function(x) x$upper1000)))
  upper500_contain_v = c(upper500_contain_v, mean(sapply(p_result, function(x) x$upper500)))
  upper200_contain_v = c(upper200_contain_v, mean(sapply(p_result, function(x) x$upper200)))
  upper100_contain_v = c(upper100_contain_v, mean(sapply(p_result, function(x) x$upper100)))
  upper50_contain_v = c(upper50_contain_v, mean(sapply(p_result, function(x) x$upper50)))
  upper25_contain_v = c(upper25_contain_v, mean(sapply(p_result, function(x) x$upper25)))
  upper10_contain_v = c(upper10_contain_v, mean(sapply(p_result, function(x) x$upper10)))
  upper5_contain_v = c(upper5_contain_v, mean(sapply(p_result, function(x) x$upper5)))
}

result_df_logistic_pred_num = data.frame(N_pred =N_pred,
           Upper5 = upper5_contain_v,
           Upper10 = upper10_contain_v,
           Upper25 = upper25_contain_v,
           Upper50 = upper50_contain_v,
           Upper100 = upper100_contain_v,
           Upper200 = upper200_contain_v,
           Upper500 = upper500_contain_v,
           Upper1000 = upper1000_contain_v,
           upper5000 = upper5000_contain_v,
           scb = scb_contain_v
           )
result_df_logistic_pred_num
if(save){
  save.image("regression_outcome_bootstrap_diff_discrete_grid.RData")
}

```