---
title: "regression_coefficient_sim Fig.10."
author: "Junting Ren"
date: "1/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../functions/simulate_genetic_data.r")
source("../functions/plot_cs.R")
source("../functions/SCB_to_CS.R")
source("../functions/regression_outcome_scb.R")
library(tidyverse)
library(doParallel)
```

# This simulation replicates Fig.10. in the paper
Fig.10. Regression coefficient simulation confidence sets coverage rate for different number of levels for inverse upper excursion sets.

# Simulations 
## Parameter setup
```{r}
write = T
set.seed(2022)
n_sim = 5000
n_boot= 1000
alpha = 0.05
var = 1 # variance for X covariance matrix
sd_error = 1 # sd for data error term 
num_levels = 8000
model = "y ~ ."
```



## With fix sample size but different number of coefficients
```{r}
beta_num_vec =c(10,25, 100,200)
#beta_num_vec =c(10,50)
beta_list = list()
n = 2000
#NVec =c(200 )
cl <- makeCluster(detectCores()-1)
registerDoParallel(cl)
scb_contain_v = c()
upper8000_contain_v = c()
upper5000_contain_v = c()
upper2000_contain_v = c()
upper1000_contain_v = c()
upper500_contain_v = c()
upper200_contain_v = c()
upper100_contain_v = c()
upper50_contain_v = c()
upper25_contain_v = c()
upper10_contain_v = c()
upper5_contain_v = c()
i = 1
for(beta_num in beta_num_vec){
  #beta = rnorm(beta_num)
  set.seed(2022)
  beta = rnorm(beta_num)
  # Correlation matrix for the X
  cor_matrix = ar1_cor(beta_num - 1,0.4)
  covariance = var* cor_matrix
  levels = seq(min(beta), max(beta), length.out = num_levels)
  beta_list[[i]] = beta
  i = i + 1
  p_result = foreach(t=1:n_sim,.errorhandling = "pass", 
                          .inorder = F,.verbose	=F, .packages = "tidyverse", .export = "plot_cs") %dopar% {
    X = cbind(rep(1,n), MASS::mvrnorm(n = n, mu = rep(0,dim(covariance)[1]),Sigma = covariance))
    y = X %*% beta +rnorm(n, sd = sd_error)
    df_fit = data.frame(y= y, X[,-1])
    SCB =  cbind(SCB_regression_coef(df_fit = df_fit, model = model, n_boot = n_boot, alpha = 0.05), beta_true = beta)
    confidence_set = scb_to_cs(SCB$UpperBound,SCB$LowerBound, levels = levels,
                               true_mean = SCB$beta_true, return_contain_only = T)
    upper8000 = confidence_set$contain_all
    upper5000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 5000)])
    upper2000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 2000)])
    upper1000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 1000)])
    upper500 = all(confidence_set$contain_individual[sample(1:num_levels, size = 500)])
    upper200 = all(confidence_set$contain_individual[sample(1:num_levels, size = 200)])
    upper100 = all(confidence_set$contain_individual[sample(1:num_levels, size = 100)])
    upper50 = all(confidence_set$contain_individual[sample(1:num_levels, size = 50)])
    upper25 = all(confidence_set$contain_individual[sample(1:num_levels, size = 25)])
    upper10 = all(confidence_set$contain_individual[sample(1:num_levels, size = 10)])
    upper5 = all(confidence_set$contain_individual[sample(1:num_levels, size = 5)])
    cover_scb  = SCB %>% 
      mutate(contain = beta_true > LowerBound & beta_true < UpperBound) %>% 
      pull(contain) %>% 
      all()
    list(upper8000 = upper8000, upper5000= upper5000,
         upper2000= upper2000, upper1000 = upper1000,
         upper500 = upper500, upper200 = upper200,
         upper100 = upper100,
         upper50 = upper50,
         upper25 = upper25,
         upper10 = upper10,
         upper5 = upper5,
         cover_scb =cover_scb
         )
    # list(cover_scb = cover_scb)
  }
  scb_contain_v = c(scb_contain_v,mean(sapply(p_result, function(x) x$cover_scb)))
  upper8000_contain_v = c(upper8000_contain_v, mean(sapply(p_result, function(x) x$upper8000)))
  upper5000_contain_v = c(upper5000_contain_v, mean(sapply(p_result, function(x) x$upper5000)))
  upper2000_contain_v = c(upper2000_contain_v, mean(sapply(p_result, function(x) x$upper2000)))
  upper1000_contain_v = c(upper1000_contain_v, mean(sapply(p_result, function(x) x$upper1000)))
  upper500_contain_v = c(upper500_contain_v, mean(sapply(p_result, function(x) x$upper500)))
  upper200_contain_v = c(upper200_contain_v, mean(sapply(p_result, function(x) x$upper200)))
  upper100_contain_v = c(upper100_contain_v, mean(sapply(p_result, function(x) x$upper100)))
  upper50_contain_v = c(upper50_contain_v, mean(sapply(p_result, function(x) x$upper50)))
  upper25_contain_v = c(upper25_contain_v, mean(sapply(p_result, function(x) x$upper25)))
  upper10_contain_v = c(upper10_contain_v, mean(sapply(p_result, function(x) x$upper10)))
  upper5_contain_v = c(upper5_contain_v, mean(sapply(p_result, function(x) x$upper5)))
}

result_df_diff_beta = data.frame(beta_num =beta_num_vec,
           upper5 = upper5_contain_v,
           upper10 = upper10_contain_v,
           upper25 = upper25_contain_v,
           upper50 = upper50_contain_v,
           upper100 = upper100_contain_v,
           upper200 = upper200_contain_v,
           upper500 = upper500_contain_v,
           upper1000 = upper1000_contain_v,
           upper2000 = upper2000_contain_v,
           upper5000 = upper5000_contain_v,
           upper8000 = upper8000_contain_v,
           scb = scb_contain_v
           )
result_df_diff_beta
#save.image("regression_coef_result.RData")
```

```{r}
beta_list
```


## With fix number (50) of coefficients but different sample size
```{r}
M = 50
set.seed(2022)
# Correlation matrix for the X
cor_matrix = ar1_cor(M - 1,0.4)
covariance = var* cor_matrix
beta = rnorm(M)
print(beta)
levels = seq(min(beta), max(beta), length.out = num_levels)
```
Showcase of SCB for coefficients
```{r}
n = 500
X = cbind(rep(1,n), MASS::mvrnorm(n = n, mu = rep(0,dim(covariance)[1]),Sigma = covariance))
y = X %*% beta +rnorm(n, sd = sd_error)
df_fit = data.frame(y= y, X[,-1])
SCB = cbind(SCB_regression_coef(df_fit = df_fit, model = model, n_boot = n_boot, alpha = 0.05), beta_true = beta)
beta_names = paste("beta", 0:(M-1),sep = "")
source("../functions/plot_cs.R")
#debug(plot_cs)
plot_cs(SCB = list(scb_up = SCB$UpperBound, scb_low = SCB$LowerBound), x = beta_names,levels = c(-2, -0.5, -0.1, 0.2), mu_true = beta, mu_hat = SCB$Mean)
```


```{r}
NVec =c(200,500, 1000,2000, 4000)
#NVec =c(200 )
scb_contain_v = c()
upper8000_contain_v = c()
upper5000_contain_v = c()
upper2000_contain_v = c()
upper1000_contain_v = c()
upper500_contain_v = c()
upper200_contain_v = c()
upper100_contain_v = c()
upper50_contain_v = c()
upper25_contain_v = c()
upper10_contain_v = c()
upper5_contain_v = c()
i = 1
for(n in NVec){
  #beta = rnorm(beta_num)
  p_result = foreach(t=1:n_sim,.errorhandling = "pass", 
                          .inorder = F,.verbose	=F, .packages = "tidyverse", .export = "plot_cs") %dopar% {
    X = cbind(rep(1,n), MASS::mvrnorm(n = n, mu = rep(0,dim(covariance)[1]),Sigma = covariance))
    y = X %*% beta +rnorm(n, sd = sd_error)
    df_fit = data.frame(y= y, X[,-1])
    SCB =  cbind(SCB_regression_coef(df_fit = df_fit, model = model, n_boot = n_boot, alpha = 0.05), beta_true = beta)
    confidence_set = scb_to_cs(SCB$UpperBound,SCB$LowerBound, levels = levels,
                               true_mean = SCB$beta_true, return_contain_only = T)
    upper8000 = confidence_set$contain_all
    upper5000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 5000)])
    upper2000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 2000)])
    upper1000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 1000)])
    upper500 = all(confidence_set$contain_individual[sample(1:num_levels, size = 500)])
    upper200 = all(confidence_set$contain_individual[sample(1:num_levels, size = 200)])
    upper100 = all(confidence_set$contain_individual[sample(1:num_levels, size = 100)])
    upper50 = all(confidence_set$contain_individual[sample(1:num_levels, size = 50)])
    upper25 = all(confidence_set$contain_individual[sample(1:num_levels, size = 25)])
    upper10 = all(confidence_set$contain_individual[sample(1:num_levels, size = 10)])
    upper5 = all(confidence_set$contain_individual[sample(1:num_levels, size = 5)])
    cover_scb  = SCB %>% 
      mutate(contain = beta_true > LowerBound & beta_true < UpperBound) %>% 
      pull(contain) %>% 
      all()
    list(upper8000 = upper8000, upper5000= upper5000,
         upper2000= upper2000, upper1000 = upper1000,
         upper500 = upper500, upper200 = upper200,
         upper100 = upper100,
         upper50 = upper50,
         upper25 = upper25,
         upper10 = upper10,
         upper5 = upper5,
         cover_scb =cover_scb
         )
    # list(cover_scb = cover_scb)
  }
  scb_contain_v = c(scb_contain_v,mean(sapply(p_result, function(x) x$cover_scb)))
  upper8000_contain_v = c(upper8000_contain_v, mean(sapply(p_result, function(x) x$upper8000)))
  upper5000_contain_v = c(upper5000_contain_v, mean(sapply(p_result, function(x) x$upper5000)))
  upper2000_contain_v = c(upper2000_contain_v, mean(sapply(p_result, function(x) x$upper2000)))
  upper1000_contain_v = c(upper1000_contain_v, mean(sapply(p_result, function(x) x$upper1000)))
  upper500_contain_v = c(upper500_contain_v, mean(sapply(p_result, function(x) x$upper500)))
  upper200_contain_v = c(upper200_contain_v, mean(sapply(p_result, function(x) x$upper200)))
  upper100_contain_v = c(upper100_contain_v, mean(sapply(p_result, function(x) x$upper100)))
  upper50_contain_v = c(upper50_contain_v, mean(sapply(p_result, function(x) x$upper50)))
  upper25_contain_v = c(upper25_contain_v, mean(sapply(p_result, function(x) x$upper25)))
  upper10_contain_v = c(upper10_contain_v, mean(sapply(p_result, function(x) x$upper10)))
  upper5_contain_v = c(upper5_contain_v, mean(sapply(p_result, function(x) x$upper5)))
}

result_df_diff_n = data.frame(N =NVec,
           upper5 = upper5_contain_v,
           upper10 = upper10_contain_v,
           upper25 = upper25_contain_v,
           upper50 = upper50_contain_v,
           upper100 = upper100_contain_v,
           upper200 = upper200_contain_v,
           upper500 = upper500_contain_v,
           upper1000 = upper1000_contain_v,
           upper2000 = upper2000_contain_v,
           upper5000 = upper5000_contain_v,
           upper8000 = upper8000_contain_v,
           scb = scb_contain_v
           )
result_df_diff_n
if(write){
  save.image("regression_coef_result.RData")
}
```
