---
title: "Simulation_analysis_linear_regression_outcome non-bootstrap"
author: "Junting Ren"
date: "12/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(doParallel) # for parallel computing
source("../functions/SCB_dense.R")
source("../functions/SCB_to_CS.R")
source("../functions/plot_cs.R")
source("../functions/noises.R") # for the noise functions
# This function is based on "Simultaneous Statistical Inference by Miller" page 124, Working-Hotelling method
simultaneous_CBs <- function(linear_model, newdata, level = 0.95){
    # Working-Hotelling 1 – α confidence bands for the model linear_model
    # at points newdata with α = 1 - level
    # estimate of residual standard error
    lm_summary <- summary(linear_model)
    # degrees of freedom 
    p <- lm_summary$df[1]
    # residual degrees of freedom
    nmp <-lm_summary$df[2]
    # F-distribution
    Fvalue <- qf(level,p,nmp)
    # multiplier
    W <- sqrt(p*Fvalue)
    # confidence intervals for the mean response at the new points
    CI <- predict(linear_model, newdata, se.fit = TRUE, interval = "confidence", 
                  level = level)
    # mean value at new points
    Y_h <- CI$fit[,1]
    # Working-Hotelling 1 – α confidence bands
    LB <- Y_h - W*CI$se.fit
    UB <- Y_h + W*CI$se.fit
    sim_CB <- data.frame(LowerBound = LB, Mean = Y_h, UpperBound = UB, newdata)
    return(sim_CB)
}

expit = function(x){
  1/(1+exp(-x))
}

simultaneous_CB_logistic <- function(linear_model, newdata, level = 0.95){
  # Working-Hotelling 1 – α confidence bands for the model linear_model
  # at points newdata with α = 1 - level
    # estimate of residual standard error
    lm_summary <- summary(linear_model)
    # degrees of freedom 
    p <- lm_summary$df[1]
    # residual degrees of freedom
    nmp <-lm_summary$df[2]
    # F-distribution
    Fvalue <- qf(level,p,nmp)
    # multiplier
    W <- sqrt(p*Fvalue)
    # confidence intervals for the mean response at the new points
    CI <- predict(linear_model, newdata, se.fit = TRUE,
                  level = level)
    # mean value at new points
    Y_h <- CI$fit
    # Working-Hotelling 1 – α confidence bands
    LB <- Y_h - W*CI$se.fit
    UB <- Y_h + W*CI$se.fit
    sim_CB <- data.frame(LowerBound = expit(LB), Mean = expit(Y_h), UpperBound = expit(UB), newdata)
    return(sim_CB)
}
```

# This simulation is not in the paper. Uses non-bootstrap method to get the SCI for regression

The working-hotelling method is for $x^d \in \mathbb{R}^d$, so for any predictor with support smaller than is going to be conservative. But it seems that we only need to have something between (-1,1) to achieve nominal coverage.

# Simulation to confirm the SCB for linear regression is valid

```{r}
n = 500
n_sim = 5
contain_v = c()
beta = c(2,1,-2)
for(i in 1:n_sim){
    #X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
    X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
    y_true = X %*% beta
    y =  X %*% beta + rnorm(n, sd=2)
    data_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
    fit = lm(y ~ x1+x2,data_fit)
    new_data =as.matrix(cbind(x0 = rep(1,2000), expand.grid(x1 = seq(-4,4,length.out = 100), x2 =  seq(-4,4,length.out = 100)) ))
    y_true_new_data = new_data %*% beta
    contain_v = c(contain_v,
                  cbind(simultaneous_CBs(fit, newdata = data.frame(new_data[,-1])), y_true_new_data) %>% 
                      mutate(contain = y_true_new_data > LowerBound & y_true_new_data < UpperBound) %>% 
                      pull(contain) %>% 
                      all()
    )
}
mean(contain_v)
```

# Simulation to confirm the SCB for logistic regression is valid
```{r}
n = 500
n_sim = 5
contain_v = c()
beta = c(0.5,1,-1)
for(i in 1:n_sim){
    #X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
    X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
    linear = X %*% beta
    y = rep(0,n)
    y_true = rep(0,n)
    for(i in 1:n){
      y[i] = rbinom(1,1, prob = 1/(1+exp(-linear[i])))
      y_true[i] = 1/(1+exp(-linear[i]))
    }
    fit = glm(y ~ X[,-1], family = binomial())
    contain_v = c(contain_v,
                  cbind(simultaneous_CB_logistic(fit, newdata = data.frame(X[,-1])), y_true) %>% 
                      mutate(contain = y_true > LowerBound & y_true < UpperBound) %>% 
                      pull(contain) %>% 
                      all()
    )
}
mean(contain_v)
```

The coverage is a bit high, this might be due to the fact that we did not cover the whole X space (since we are using the sample X).

# linear regression simulation for confidence set
Here is the model we are going to simulate from 
$$
y = \beta_0 + \beta_1 x_1 + \beta_2x_1^2 + \beta_3x_1^3+\beta_4 x_2 + \beta_5 x_2^2 + \beta_6x_2^3 + \epsilon
$$
The plotting is going to be a 2d plane (x1, x2) with colors indicating the y values.

```{r}
num_levels = 5000
n_sim = 5
beta = c(2,1,0.5,-1.2, -0.5, 1.8, 1.1)
sd_error = 2
x1 =  seq(-1,1,length.out = 100)
x2 = seq(-1,1,length.out = 100)
new_data =as.matrix(cbind(x0 = rep(1,100*100), expand.grid(x1 = x1, x2 =  x2) ))
y_true_new_data = new_data[,1]*beta[1] + new_data[,2]*beta[2]+(new_data[,2]^2)*beta[3] +(new_data[,2]^3)*beta[4] +
  (new_data[,3])*beta[5] +  (new_data[,3]^2)*beta[6] +  (new_data[,3]^3)*beta[7]
true_mean_matrix = data.frame(new_data, y_true = y_true_new_data) %>% dplyr::select(x1,x2, y_true)%>% 
      pivot_wider(names_from = x2, values_from = y_true) %>% column_to_rownames("x1") %>% as.matrix()
levels = seq(min(y_true_new_data), max(y_true_new_data), length.out = num_levels)
level_alpah = 0.2
random_level = T #whether the levels are random or just quantiles of the data
```

## Showcase of confidence set 
```{r}
n = 200
X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 =  rnorm(n))
y =  X[,1]*beta[1] + X[,2]*beta[2]+(X[,2]^2)*beta[3] +(X[,2]^3)*beta[4] +
  (X[,3])*beta[5] +  (X[,3]^2)*beta[6] +  (X[,3]^3)*beta[7]+ rnorm(n, sd=sd_error)
data_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
fit = lm(y ~ poly(x1,3)+poly(x2,3),data_fit)
SCB = cbind(simultaneous_CBs(fit, newdata = data.frame(new_data[,-1]), level = 1 - level_alpah),y_true = y_true_new_data)
est_matrix = SCB %>% select(x1,x2, Mean)%>% 
      pivot_wider(names_from = x2, values_from = Mean) %>% column_to_rownames("x1") %>% as.matrix()
scb_up_matrix = SCB %>% select(x1,x2, UpperBound)%>% 
      pivot_wider(names_from = x2, values_from = UpperBound) %>% column_to_rownames("x1") %>% as.matrix()
scb_low_matrix = SCB %>% select(x1,x2, LowerBound)%>% 
      pivot_wider(names_from = x2, values_from = LowerBound) %>% column_to_rownames("x1") %>% as.matrix()
confidence_set = scb_to_cs(scb_up_matrix,scb_low_matrix, levels = c(1,1.5,2,3,4,5),x1 = x1, x2 = x2,
                              true_mean = true_mean_matrix, est_mean = est_matrix, return_contain_only = T, return_plot = T)
confidence_set$plot_cs
```


## Start the simulation
```{r}
NVec =c(50, 100, 200, 300, 400,500)
#NVec =c(20 )
cl <- makeCluster(detectCores()-1)
registerDoParallel(cl)
scb_contain_v = c()
upper5000_contain_v = c()
upper1000_contain_v = c()
upper500_contain_v = c()
upper200_contain_v = c()
upper100_contain_v = c()
upper50_contain_v = c()
upper25_contain_v = c()
upper10_contain_v = c()
upper5_contain_v = c()

for(n in NVec){
  p_result = foreach(t=1:n_sim,.errorhandling = "pass", 
                          .inorder = F,.verbose	=F, .packages = "tidyverse", .export = "plot_cs") %dopar% {
    #X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
    X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 =  rnorm(n))
    y =  X[,1]*beta[1] + X[,2]*beta[2]+(X[,2]^2)*beta[3] +(X[,2]^3)*beta[4] +
      (X[,3])*beta[5] +  (X[,3]^2)*beta[6] +  (X[,3]^3)*beta[7]+ rnorm(n, sd=sd_error)
    data_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
    fit = lm(y ~ poly(x1,3)+poly(x2,3),data_fit)
    SCB = cbind(simultaneous_CBs(fit, newdata = data.frame(new_data[,-1]), level = 1 - level_alpah),y_true = y_true_new_data)
    scb_up_matrix = SCB %>% select(x1,x2, UpperBound)%>% 
      pivot_wider(names_from = x2, values_from = UpperBound) %>% column_to_rownames("x1") %>% as.matrix()
    scb_low_matrix = SCB %>% select(x1,x2, LowerBound)%>% 
      pivot_wider(names_from = x2, values_from = LowerBound) %>% column_to_rownames("x1") %>% as.matrix()
    confidence_set = scb_to_cs(scb_up_matrix,scb_low_matrix, levels = levels,
                               true_mean = true_mean_matrix, return_contain_only = T)
    upper5000 = confidence_set$contain_all
    if(random_level){
      upper1000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 1000)])
      upper500= all(confidence_set$contain_individual[sample(1:num_levels, size = 500)])
      upper200 = all(confidence_set$contain_individual[sample(1:num_levels, size = 200)])
      upper100 = all(confidence_set$contain_individual[sample(1:num_levels, size = 100)])
      upper50 = all(confidence_set$contain_individual[sample(1:num_levels, size = 50)])
      upper25 = all(confidence_set$contain_individual[sample(1:num_levels, size = 25)])
      upper10 = all(confidence_set$contain_individual[sample(1:num_levels, size = 10)])
      upper5 = all(confidence_set$contain_individual[sample(1:num_levels, size = 5)])
    }else{
      upper1000 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 1000)])
      upper500= all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 500)])
      upper200 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 200)])
      upper100 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 100)])
      upper50 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 50)])
      upper25 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 25)])
      upper10 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 10)])
      upper5 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 5)])
    }
    cover_scb  = SCB %>% 
      mutate(contain = y_true_new_data > LowerBound & y_true_new_data < UpperBound) %>% 
      pull(contain) %>% 
      all()
    list(upper5000 = upper5000, upper1000= upper1000,
         upper500= upper500, upper200 = upper200,
         upper100 = upper100, upper50 = upper50,
         upper25 = upper25,
         upper10 = upper10, upper5 =upper5,
         cover_scb =cover_scb
         )
    # list(cover_scb = cover_scb)
  }
  scb_contain_v = c(scb_contain_v,mean(sapply(p_result, function(x) x$cover_scb)))
  upper5000_contain_v = c(upper5000_contain_v, mean(sapply(p_result, function(x) x$upper5000)))
  upper1000_contain_v = c(upper1000_contain_v, mean(sapply(p_result, function(x) x$upper1000)))
  upper500_contain_v = c(upper500_contain_v, mean(sapply(p_result, function(x) x$upper500)))
  upper200_contain_v = c(upper200_contain_v, mean(sapply(p_result, function(x) x$upper200)))
  upper100_contain_v = c(upper100_contain_v, mean(sapply(p_result, function(x) x$upper100)))
  upper50_contain_v = c(upper50_contain_v, mean(sapply(p_result, function(x) x$upper50)))
  upper25_contain_v = c(upper25_contain_v, mean(sapply(p_result, function(x) x$upper25)))
  upper10_contain_v = c(upper10_contain_v, mean(sapply(p_result, function(x) x$upper10)))
  upper5_contain_v = c(upper5_contain_v, mean(sapply(p_result, function(x) x$upper5)))
}

result_df_linear = data.frame(N =NVec,
           Upper5 = upper5_contain_v,
           Upper10 = upper10_contain_v,
           Upper25 = upper25_contain_v,
           Upper50 = upper50_contain_v,
           Upper100 = upper100_contain_v,
           Upper200 = upper200_contain_v,
           Upper500 = upper500_contain_v,
           Upper1000 = upper1000_contain_v,
           upper5000 = upper5000_contain_v,
           scb = scb_contain_v
           )
result_df_linear
```



# Logistic regression simulation for confidence set
Here is the model we are going to simulate from 
$$
logit(x) = \beta_0 + \beta_1 x_1 + \beta_2x_1^2 + \beta_3x_1^3+\beta_4 x_2 + \beta_5 x_2^2 + \beta_6x_2^3 
$$
The plotting is going to be a 2d plane (x1, x2) with colors indicating the y values.

```{r}
# have to make sure that extreme values do not overshoots the expit, or else the model will not be able to estimate the coeffcient accurately.
beta = c(-1,1,0.5,-1.1, -0.5, 0.81, -1.1)
level_alpah = 0.4
x1 =  seq(-1,1,length.out = 100)
x2 = seq(-1,1,length.out = 100)
new_data =as.matrix(cbind(x0 = rep(1,100*100), expand.grid(x1 = x1, x2 =  x2) )) # grid of the data for constructing the SCB
y_true_new_data = expit(new_data[,1]*beta[1] + new_data[,2]*beta[2]+(new_data[,2]^2)*beta[3] +(new_data[,2]^3)*beta[4] +
  (new_data[,3])*beta[5] +  (new_data[,3]^2)*beta[6] +  (new_data[,3]^3)*beta[7])
true_mean_matrix = data.frame(new_data, y_true = y_true_new_data) %>% dplyr::select(x1,x2, y_true)%>% 
      pivot_wider(names_from = x2, values_from = y_true) %>% column_to_rownames("x1") %>% as.matrix()
levels = seq(min(y_true_new_data), max(y_true_new_data), length.out = num_levels)
random_level = T #whether the levels are random or just quantiles of the data
```

## Showcase of confidence set 
```{r}
n = 500
X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
linear = X[,1]*beta[1] + X[,2]*beta[2]+(X[,2]^2)*beta[3] +(X[,2]^3)*beta[4] +
  (X[,3])*beta[5] +  (X[,3]^2)*beta[6] +  (X[,3]^3)*beta[7]
y = rep(0,n)
y_true = rep(0,n)
for(i in 1:n){
  y[i] = rbinom(1,1, prob = 1/(1+exp(-linear[i])))
  y_true[i] = 1/(1+exp(-linear[i]))
}
data_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
fit = glm(y ~ poly(x1,3) + poly(x2,3), family = binomial(), data = data_fit)
SCB = cbind(simultaneous_CB_logistic(fit, newdata = data.frame(new_data[,-1]), level = 1- level_alpah), y_true_new_data) 
scb_up_matrix = SCB %>% select(x1,x2, UpperBound)%>%
  pivot_wider(names_from = x2, values_from = UpperBound) %>% column_to_rownames("x1") %>% as.matrix()
scb_low_matrix = SCB %>% select(x1,x2, LowerBound)%>%
  pivot_wider(names_from = x2, values_from = LowerBound) %>% column_to_rownames("x1") %>% as.matrix()
est_matrix = SCB %>% select(x1,x2, Mean)%>% 
    pivot_wider(names_from = x2, values_from = Mean) %>% column_to_rownames("x1") %>% as.matrix()
confidence_set = scb_to_cs(scb_up_matrix,scb_low_matrix, levels = c(0.1, 0.2, 0.4,0.5, 0.6),x1 = x1, x2 = x2,
                           true_mean = true_mean_matrix, est_mean = est_matrix,return_contain_only = T, return_plot = T)
confidence_set$plot_cs
```


## Start the simulation
```{r}
#NVec =c(5000)
cl <- makeCluster(detectCores()-1)
registerDoParallel(cl)
scb_contain_v = c()
upper5000_contain_v = c()
upper1000_contain_v = c()
upper500_contain_v = c()
upper200_contain_v = c()
upper100_contain_v = c()
upper50_contain_v = c()
upper25_contain_v = c()
upper10_contain_v = c()
upper5_contain_v = c()

for(n in NVec){
  p_result = foreach(t=1:n_sim,.errorhandling = "pass", 
                          .inorder = F,.verbose	=F, .packages = "tidyverse", .export = "plot_cs") %dopar% {
    #X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 = rnorm(n))
    X = cbind(x0 = rep(1,n), x1 = rnorm(n), x2 =  rnorm(n))
    linear =  X[,1]*beta[1] + X[,2]*beta[2]+(X[,2]^2)*beta[3] +(X[,2]^3)*beta[4] +
      (X[,3])*beta[5] +  (X[,3]^2)*beta[6] +  (X[,3]^3)*beta[7]
    y = rep(0,n)
    for(i in 1:n){
      y[i] = rbinom(1,1, prob = 1/(1+exp(-linear[i])))
    }
    data_fit = data.frame(y, dplyr::select(data.frame(X), x1, x2))
    fit =  glm(y ~ poly(x1,3) + poly(x2,3), family = binomial(), data = data_fit)
    SCB = cbind(simultaneous_CB_logistic(fit, newdata = data.frame(new_data[,-1]), level = 1- level_alpah),y_true = y_true_new_data)
    scb_up_matrix = SCB %>% select(x1,x2, UpperBound)%>% 
      pivot_wider(names_from = x2, values_from = UpperBound) %>% column_to_rownames("x1") %>% as.matrix()
    scb_low_matrix = SCB %>% select(x1,x2, LowerBound)%>% 
      pivot_wider(names_from = x2, values_from = LowerBound) %>% column_to_rownames("x1") %>% as.matrix()
    confidence_set = scb_to_cs(scb_up_matrix,scb_low_matrix, levels = levels,
                               true_mean = true_mean_matrix, return_contain_only = T)
    upper5000 = confidence_set$contain_all
    if(random_level){
      upper1000 = all(confidence_set$contain_individual[sample(1:num_levels, size = 1000)])
      upper500= all(confidence_set$contain_individual[sample(1:num_levels, size = 500)])
      upper200 = all(confidence_set$contain_individual[sample(1:num_levels, size = 200)])
      upper100 = all(confidence_set$contain_individual[sample(1:num_levels, size = 100)])
      upper50 = all(confidence_set$contain_individual[sample(1:num_levels, size = 50)])
      upper25 = all(confidence_set$contain_individual[sample(1:num_levels, size = 25)])
      upper10 = all(confidence_set$contain_individual[sample(1:num_levels, size = 10)])
      upper5 = all(confidence_set$contain_individual[sample(1:num_levels, size = 5)])
    }else{
      upper1000 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 1000)])
      upper500= all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 500)])
      upper200 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 200)])
      upper100 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 100)])
      upper50 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 50)])
      upper25 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 25)])
      upper10 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 10)])
      upper5 = all(confidence_set$contain_individual[
        seq.int(quantile(1:num_levels,0.05),quantile(1:num_levels,0.95), length.out = 5)])
    }
    cover_scb  = SCB %>% 
      mutate(contain = y_true_new_data > LowerBound & y_true_new_data < UpperBound) %>% 
      pull(contain) %>% 
      all()
    list(upper5000 = upper5000, upper1000= upper1000,
         upper500= upper500, upper200 = upper200,
         upper100 = upper100, upper50 = upper50,
         upper25 = upper25,
         upper10 = upper10, upper5 =upper5,
         cover_scb =cover_scb
         )
    # list(cover_scb = cover_scb)
  }
  scb_contain_v = c(scb_contain_v,mean(sapply(p_result, function(x) x$cover_scb)))
  upper5000_contain_v = c(upper5000_contain_v, mean(sapply(p_result, function(x) x$upper5000)))
  upper1000_contain_v = c(upper1000_contain_v, mean(sapply(p_result, function(x) x$upper1000)))
  upper500_contain_v = c(upper500_contain_v, mean(sapply(p_result, function(x) x$upper500)))
  upper200_contain_v = c(upper200_contain_v, mean(sapply(p_result, function(x) x$upper200)))
  upper100_contain_v = c(upper100_contain_v, mean(sapply(p_result, function(x) x$upper100)))
  upper50_contain_v = c(upper50_contain_v, mean(sapply(p_result, function(x) x$upper50)))
  upper25_contain_v = c(upper25_contain_v, mean(sapply(p_result, function(x) x$upper25)))
  upper10_contain_v = c(upper10_contain_v, mean(sapply(p_result, function(x) x$upper10)))
  upper5_contain_v = c(upper5_contain_v, mean(sapply(p_result, function(x) x$upper5)))
}

result_df_logistic = data.frame(N =NVec,
           Upper5 = upper5_contain_v,
           Upper10 = upper10_contain_v,
           Upper25 = upper25_contain_v,
           Upper50 = upper50_contain_v,
           Upper100 = upper100_contain_v,
           Upper200 = upper200_contain_v,
           Upper500 = upper500_contain_v,
           Upper1000 = upper1000_contain_v,
           upper5000 = upper5000_contain_v,
           scb = scb_contain_v
           )
result_df_logistic
save.image("regression_outcome_non_bootstrap.RData")
```
